Working title, The impact of heterospecific pollen on plant reproductive success is mediated by phylogenetic distance and floral reproductive traits

### 2018-11-29 Manuscript_draft/Manuscript_draft.Rmd
regression line, mixed effect flower level, each one was a random one. Ask this to Nacho to confirm...

Recent important studies have advanced in the ecological importance of heterospecific pollen effect @morales2008 @ashamn2013 @arceo2016. A general overview of it can reduce species fitness (REFS) but not in al the cases (Refs). Other general facts... Quantity of foreign pollen that arrives...

>>>>

Recent important studies have advanced in the ecological importance of heterospecific pollen effect @morales2008 @ashamn2013 @arceo2016. A general overview of heterospecific pollen effect is that it can play an important role on species fitness but seems to be context dependent and not always fitness decreased is produced. There are several traits that are postulated to be highly relevant to this process. However the relative importance of them and their contribution to this effect is not yet well understood.

can reduce species fitness (REFS) but seems to be highly contex-dependent. There are hypothesized that some traits can play a crucial role in this species interaction such as stigma type, pollen size,
